---
title: "course 9 peer assignment"
author: "Sandra van de Beld"
date: "23-12-2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## introduction
I have made an interactive app. 
The app consist of the following: 
- selection of datasets: you can choose from 3 different datasets
- selection of number of rows shown: you can choose how many rows you want to see in the head() function
- a summary table that shows the statistics of the dataset that is chosen
- the dataframe, you see the number of rows that are selected


## example of the summary table shown in the shiny app
The example below shows the summary table for the pressure dataset, this dataset is one of the datasets that can be chosen from within the shiny app. 

```{r}
summary(pressure)
```

## example of the dataframe shown in the shiny app
the expample below shows the dataframe with 10 rows, the number of rows can be chosen witin the shiny app

```{r pressure, echo=TRUE}
head(cars, 10)
```

